DCM_investigation

### 2020-11-05 article_figures_ARTHUR_CAPET.Rmd
update fig

ms<-ggmap(myMap_stamen)
ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)))+
  facet_wrap(~monthn, scale="fixed")+
  theme_bw()+
  scale_color_discrete(name="", labels=c('non-DCM','DCM'))+
  theme(legend.position = 'top', legend.box = "horizontal")+
  scale_x_continuous(name='', breaks = c(27,30,33,36,39), limits = c(27,42), expand = expand_scale(add = 0))+
  scale_y_continuous(name='', breaks = seq(41,47), limits = c(40.7,47), expand = expand_scale(add = 0))

>>>>

ms<-ggmap(myMap_stamen)
ms1<-ms+geom_point(data=tmp_fitco, aes(x=lon,y=lat, color=factor(dcm_or_not)), alpha=.6)+
  facet_wrap(~monthn, scale="fixed")+
  theme_bw()+
  #scale_color_discrete(name="", labels=c('non-DCM','DCM'))+
  scale_color_manual(values = c("black", "red"), labels=c('non-DCM','DCM'), name="")+
  theme(legend.position = 'top', legend.box = "horizontal")+
  scale_x_continuous(name='', breaks = c(27,30,33,36,39), limits = c(27,42), expand = expand_scale(add = 0))+
  scale_y_continuous(name='', breaks = seq(41,47), limits = c(40.7,47), expand = expand_scale(add = 0)) +
  # for another wrap colour (B/W instead of grey)
  theme(panel.background=element_rect(fill='white', colour='black'),strip.background=element_rect(fill='white', colour='black'))
